
\section{Uniqueness among classical solutions}

	\paragraph{On the importance of uniqueness results}
	\label{importance uniqueness}
	
	The seasoned specialist in PDEs naturally asks whether the value function is the only solution to the terminal problem mentioned in theorem \ref{classical solution HJB}. Who else? Suppose we somehow computed a solution of the terminal value problem. Without any uniqueness result, we are left wondering whether or not the computed solution is also the sought value function. We immediately want to make up for this inconvenience lest the more practically inclined reader quit reading with a deprecating smile.

	\subsection{A local comparison result}
	
		Comparison results are often the key relation when showing the uniqueness of a given terminal or boundary value problem. This case is no different. Given a subsolution $ u $ and a supersolution $ v $, satisfying $ u \leq v $ on the \say{boundary} $ \{ T \} \times \mathbb{R}^N $, we extend latter relationship on some closed region. In order to do so, we examine the difference $ w \coloneqq u - v $, to find out that $ w $ is a subsolution to some other PDE described by $ F $, that is
		
		\begin{equation*}
			F(t, x, Dw) \leq 0
		\end{equation*}
		for all $ (t, x) \in \left(0, T \right) \times \mathbb{R}^N $.
		To conclude $ u \leq v $, i.e. $ w \leq 0 $ on mentioned region, we locally compare $ w $ to a strict supersolution $ \varphi : \left[ t_{\varphi}, T \right] \times \overline{\Omega^{\prime}} \to \mathbb{R} $ of $ F $, meaning
		
		\begin{equation*}
			F(t, x, D\varphi) > 0
		\end{equation*}
		
		holds for all $ (t, x) \in \left( t_{\varphi}, T \right) \times\Omega^{\prime} $. More precisely, we exclude the possibility of $ w -\varphi $ attaining a global maximum in $ \left[ t_{\varphi}, T \right) \times \Omega^{\prime} $. Excluding local extrema in ${ \left( t_{\varphi}, T \right) \times \Omega^{\prime} }$ is an immediate consequence of the conflicting sub-and supersolution inequalities of $ w $ and $ \varphi $ together with Fermat's rule, which yields $ Dw = D\varphi $ for \emph{interior} extrema of $ w - \varphi $. Unfortunately Fermat's rule does not necessarily apply to extrema of the form $ (t_{\varphi}, x^{*}) $ located in $ \{t_{\varphi} \}\times \Omega^{\prime}  $ and another strategy is needed to derive the contradiction $ F(t_{\varphi}, x^{*}, D\varphi(t_\varphi, x^{*})) \leq 0 $ . This is achieved by the means of the following, more general lemma.
		
		\subimport{./}{Supersol_comp}
	
		Having laid the technical groundwork to compare sub- and supersolutions, the proof of the following comparison result boils down to derive an appropriate PDE for $ w $ and to construct suitable strict supersolutions. But first, we define the closed regions to which will apply the theorem.
		
		\begin{definition}
			\label{regions}
			Given the interval $ \left[0, T\right] $, some point $ z_0 \in \mathbb{R}^N $ and some radius $ R > 0 $, we denote by $ \mathcal{C}_{z_0, R} $ the closed region
			
			\begin{equation*}
			\mathcal{C}_{z_0, R} \coloneqq \Bigg\{ (t, x) \in \left[ T - \frac{R}{C}, T \right] \times \mathbb{R}^N: \lvert x - z_0 \rvert + C(T-t) \leq R \Bigg\} \ .
			\end{equation*}
		\end{definition}
		
		\subimport{./}{Smooth_local_comp}
	
	\subsection{From local to global}
		In this section we want to extend our local comparison result, namely theorem \ref{smooth_loc}, to a global one. Using the Lipschitz-conditions imposed upon our problem-parameters, we can easily verify
		
		\begin{equation}
			\label{varying_Lipschitz}
			\lvert H(t, x, p) - H(t, x, q) \rvert \leq L \left(1 + \lvert x \rvert \right) \lvert p - q \rvert \ ,
		\end{equation}
		for all $ x \in \mathbb{R}^{N} $, as stated in \cite[p.~167]{zhou} and shown in \ref{Hamiltonian gradient}. The most obvious Lipschitz-constant from inequality \eqref{eqn:H1} is now given by
		\begin{equation*}
			C = C(z_0) \coloneqq L (1 + \lvert z_0 \lvert + R) \ ,
		\end{equation*}
		considering the domain $ \left(0, T \right) \times B_R(z_0) $.
		
		If the radius $ R $ remains constant, the length of the time interval spanned by $ \mathcal{C}_{z_0, R} $ tends to zero as the norm of $ z_0 $ increases. The proof of the following corollary consists in choosing a suitable radius $ R $ for each $ z_0 $, in order to cover the whole domain.
		
		\subimport{./}{Global_comp}
		